---
title: "p8105_hw6_cn2604"
author: "Cary Ni"
date: "2022-11-19"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(glmnet)
library(fastDummies)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 2

## Data cleaning
```{r}
homi_df = read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = paste(city, state, sep = ", "),
    outcome = case_when(
      disposition == 'Closed without arrest' ~ 'unsolved',
      disposition == 'Open/No arrest' ~ 'unsolved',
      disposition == 'Closed by arrest' ~ 'solved', 
      TRUE ~ 'unknown'
    )
  ) %>% 
  relocate(city_state, .after = state)

new_df = homi_df %>% 
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  filter(victim_race %in% c("White", "Black")) %>% 
  mutate(
    outcome = as.factor(outcome),
    victim_race = as.factor(victim_race),
    victim_sex = as.factor(victim_sex),
    victim_age = as.numeric(victim_age)
  ) %>% 
  na.omit()
```

## Build the model for Baltimore, MD

```{r}
baltimore_model = new_df %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(outcome ~ victim_age + victim_sex + victim_race, data =., family = "binomial")

estimate_odd = baltimore_model %>% 
  broom::tidy() %>% 
  filter(term == 'victim_sexMale') %>% 
  select(estimate) %>% 
  exp()
  
conf_odd_raw = exp(confint.default(baltimore_model))
conf_odd = conf_odd_raw['victim_sexMale',] %>% as_tibble_row()
baltimore_result = merge(estimate_odd, conf_odd)
```

## Create a function
```{r}
get_outcome = function(sample_df){
  city_model = glm(outcome ~ victim_age + victim_sex + victim_race, 
                   data = sample_df, 
                   family = "binomial")
  
  sample_odd = city_model %>% 
  broom::tidy() %>% 
  filter(term == 'victim_sexMale') %>% 
  select(estimate) %>% 
  exp()
  
  conf_odd_raw = exp(confint.default(city_model))
  conf_odd = conf_odd_raw['victim_sexMale',] %>% as_tibble_row()
  sample_result = merge(sample_odd, conf_odd)
}
```

## Pass cities to the function
```{r}
result_df = 
  new_df %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(
    city_result = map(data, get_outcome)
  ) %>% 
  unnest(city_result) %>% 
  select(-data) %>%
  set_names(c("city_state", "estimate_OR", "conf.low", "conf.high"))

```

## Create the plot for odds ratio of homicide
```{r}
result_df %>% 
  ggplot(aes(x = reorder(city_state,-estimate_OR), y = estimate_OR)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(
    title = "Odds ratio of homicide solved of male against female",
    x = "City",
    y = "Estimate Odds ratio")
```

# Problem 3

## Data cleaning
```{r}
birth_df = read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate_at(c('babysex', 'frace', 'malform', 'mrace'), as.factor) %>% 
  mutate(
    smoken = as.factor(ifelse(smoken > 0, 1, 0))
  )

sum(is.na(birth_df))
```

`'babysex', 'frace', 'malform', 'mrace'` are changed from double to factors and no missing values are found in the dataframe. 

## Cross validation to find parameters for model building
```{r}
set.seed(1)
# those categorical variables have different indicator for different levels, which needs to be uniform through converting to dummy variables
dummy_df = dummy_cols(
  birth_df, 
  select_columns = c('babysex', 'frace', 'malform', 'mrace','smoken'),
  remove_selected_columns = TRUE,
  remove_first_dummy = TRUE
  )
covariates = data.matrix(dummy_df %>% select(-bwt))
birthweight = data.matrix(dummy_df %>% select(bwt))
# 10 folds cv is used 
cv_object = cv.glmnet(covariates, birthweight, nfolds = 10)
plot(cv_object)
# Find the best lambda with lowest se
best_lambda = cv_object %>% broom::glance() %>% pull(lambda.min)

```

## Build elastic net regression model
```{r}
ela_model = glmnet(covariates, birthweight, lambda = best_lambda, alpha = 0.5)
model_coef = coef.glmnet(ela_model) %>% as.matrix() %>% as.data.frame()
model_coef[model_coef == 0] = NA
# Extract all of the non-zero variables of elastic net model
selected_var = model_coef %>% na.omit() %>% row.names()
selected_var = selected_var[-1]

final_var = dummy_df %>% select(selected_var) %>% data.matrix()
final_weight = dummy_df %>% pull(bwt)
my_model = lm(final_weight ~ final_var)
# show all of the variables
my_model %>% broom::tidy() %>% transform(term = str_replace(term, "final_var", "")) %>% knitr::kable()
```

## Plot residuals against fitted values
```{r}
birth_df %>% 
  modelr::add_residuals(my_model) %>% 
  modelr::add_predictions(my_model) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5)
```

## Compare to other two linear models
```{r}
model_1 = lm(bwt ~ blength + gaweeks, data = birth_df)
model_2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = birth_df)

# Create dataframe for cross validation
cv_result = 
  modelr::crossv_mc(dummy_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_result = 
  cv_result %>% 
  mutate(
    my_model = map(train, ~lm(bwt ~ bhead + blength + delwt + fincome + 
    gaweeks+ menarche + mheight + momage + parity + wtgain + babysex_2 + frace_4     + mrace_2 + mrace_3 + mrace_4 + smoken_1, data = .x)),
    model_1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_2 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + 
    bhead*babysex + blength*babysex+ bhead*blength*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_my = map2_dbl(my_model, test, ~rmse(model=.x, data = .y)),
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model=.x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model=.x, data = .y))
  )
  
```

## Compare rmse as an indicator of model performance
```{r}

```



